Accelerated Magnetic Resonance Imaging by Adversarial Neural Network

### 2018-01-04 paper.tex
Update all paper, see red comments

\begin{keyword}
\texttt MRI \sep GAN \sep Imaging
%\MSC[2010] 00-01\sep  99-00
\end{keyword}

@@

The compressed sensing (CS) technique~\cite{donoho2006compressed}
allows efficient acquisition and reconstruction of a signal with fewer
samples than the Nyquist-Shannon sampling theorem requires, if the
signal has sparse representation in a known transform domain. Using
CS for MRI reconstruction by sampling a small subset of the k-space
grid had been proposed in~\cite{lustig2007sparse}. The underlying
assumption is that the undersampling is random, such that the zero-filled
Fourier reconstruction exhibits incoherent artifacts that behave similarly
to additive random noise. This, however, would require specified pulse
programming.

Recently machine learning techniques based on manifold learning~\cite{usman2014compressive,bhatia2015fast}
and dictionary learning~\cite{ravishankar2011mr,caballero2014dictionary}
were suggested for MRI reconstruction. MRI reconstruction using convolutional
neural networks (CNN) was introduced in \cite{wang2016accelerating}.
The network learns the mapping between zero-filled and fully-sampled
MR images. In \cite{Oktay2016}, residual network was proposed for
MRI super-resolution. Their model is able to receive multiple inputs
acquired from different viewing planes for better image reconstruction.
Both works address the reconstruction problems in the image domain
rather than the k-space domain. The proposed framework utilizes recent
advances in deep learning, while similarly to the CS methods addresses
MRI reconstruction directly from the k-space. Specifically, we use
generative adversarial networks (GAN) \cite{goodfellow2014generative,radford2015unsupervised,pathak2016context}.
GANs are based on the inter-play between two networks: a generator
and a discriminator. The generator is capable of learning the distribution
over a data-base, and sample realizations of this distribution. The
discriminator is trained to distinguish between `generated' samples
and real ones. This powerful combination has been used for generating
Computed Tomography (CT)-like images from MRIs~\cite{nie2016medical}.
Here, the generator is used for reconstruction of the entire k-space
grid from under-sampled data. Its loss is a combination of an adversarial
loss, based on the discriminator output and a fidelity loss with respect
to the fully sampled MRI. Promising results are obtained for brain
MRI reconstruction using only 52\% of the data.

The paper is organized as follows. Section 2 presents some theoretical
foundation and our method. Section 3 describes the experimental results.
Conclusions and future directions are describes in section 4.

%--------------------- METHOD --------------------%
\section{Method}

@@

Let $s_{p}=M_{p}\odot s_{0}$ denote the under-sampled k-space. Given
a sampling mask and a model $f$, defined by the set of parameters
$\Theta$, our goal is to estimate the missing k-space samples such
that: 
\begin{equation}
\Theta=\arg\min_{\Theta}L(F^{H}f\left(s_{p};\Theta\right),\boldsymbol{u})
\end{equation}
where $L\left(\cdot\right)$ is the loss function. While choosing
the loss to be L2 norm is reasonable for natural images, for the k-space,
which has different spatial features, this may not be enough. As mentioned
in \cite{pathak2016context}, L2 minimization provides a blurry solution.
Averaging the high frequency details in the k-space domain results
in very poor reconstruction. In order to address this problem, we
used the adversarial loss, based on GAN.

@@

\begin{equation}
\begin{aligned}L_{G}=\alpha\cdot E_{\mathrm{z\sim p_{u}\left(z\right)}}\mathrm{\log\left[1-D\left(F^{-1}\left(\hat{s}_{0}\right)\right)\right]}+\\
\beta\cdot||\left(1-M_{p}\right)\odot\left(\hat{s}_{0}-s_{0}\right)||_{2}^{2}
\end{aligned}
\end{equation}
where $\hat{s}_{0}$ is the estimated k-space and $\alpha=1,\,\beta=0.8$
are hyperparameters tuned by a cross-validation process. The discriminator's
input is the reconstructed MR image,\textbf{ }i.e.,\textbf{ }after
IFFT. By that, we are integrating the reconstruction phase in our
optimization.

@@

A common architecture is used for the discriminator, composed of convolutional
layers, batch normalization, and leaky-ReLU as suggested in \cite{radford2015unsupervised}.
For the generator, we compose a dedicated architecture based on multi-channel
input for representing the real and imaginary components. Both architectures
are shown in Figure \ref{fig:test}.\textbf{ }The training methodology
is doing $k_{g}$ generator update steps for each discriminator single
step.

@@

%--------------------- Experiments --------------------%
\section{Experiments}

@@

We compare the proposed method to reconstruction results obtained by using a conventional compressed sensing method CS-MRI \cite{lustig2007sparse} and Zero-filling. In addition, we optimized two networks: 1. CNN-L2 - a k-space generator (with same architecture as the proposed method) using only L2 loss. 2. IM-CNN-L2 - a network which performs on the image-space and optimized to remove the artifacts caused by under-sampling and zero padding. We used the U-net \cite{ronneberger2015u} architecture inspired by \cite{lee2017deep}. The same sampling masks was used for all cases.

@@

%--------------------- CONCLUSIONS --------------------%
\section{Discussion}

>>>>

\begin{keyword}
\texttt MRI \sep GAN \sep Accelerated \sep K-space
%\MSC[2010] 00-01\sep  99-00
\end{keyword}

@@

The compressed sensing (CS) technique~\cite{donoho2006compressed} allows efficient acquisition and reconstruction of a signal with fewer samples than the Nyquist-Shannon sampling theorem requires, if the signal has sparse representation in a known transform domain. Using CS for MRI reconstruction by sampling a small subset of the k-space grid had been proposed in~\cite{lustig2007sparse}. The underlying assumption is that the undersampling is random, such that the zero-filled Fourier reconstruction exhibits incoherent artifacts that behave similarly to additive random noise. {\color{red}This, however, makes the algorithm less sensitive to fine details and noise like texture, results in smooth reconstruction with loss of diagnostically information, as we will see in section \ref{experiments_section}.}
%This, however, would require specified pulse programming.

Recently machine learning techniques based on manifold learning~\cite{usman2014compressive,bhatia2015fast} and dictionary learning~\cite{ravishankar2011mr,caballero2014dictionary} were suggested for MRI reconstruction. MRI reconstruction using convolutional neural networks (CNN) was introduced in \cite{wang2016accelerating}. The network learns the mapping between zero-filled and fully-sampled MR images. In \cite{Oktay2016}, residual network was proposed for MRI super-resolution. Their model is able to receive multiple inputs acquired from different viewing planes for better image reconstruction. In \cite{lee2017deep,hyun2017deep} a multi-scale residual network, also known as U-net~\cite{ronneberger2015u} is used and provides good reconstruction MR images.
Deep convolutional networks have been successfully applied to acceleration of dynamic MRI in \cite{sandinodeep}. All these works address the reconstruction problem in the image domain rather than the k-space domain.

The proposed framework utilizes recent advances in deep learning, while similarly to the CS methods addresses MRI reconstruction directly from the k-space. Specifically, we use generative adversarial networks (GAN) \cite{goodfellow2014generative,radford2015unsupervised,pathak2016context}. 
GANs are based on the inter-play between two networks: a generator and a discriminator. The generator is capable of learning the distribution over a data-base, and sample realizations of this distribution. 
The discriminator is trained to distinguish between `generated' samples and real ones. This powerful combination has been used for MRI acceleration in~\cite{yu2017deep,mardani2017deep}, and also for generating Computed Tomography (CT)-like images from MRIs~\cite{nie2016medical}.
Here, the generator is used for reconstruction of the entire k-space grid from under-sampled data. Its loss is a combination of an adversarial loss, based on the discriminator output and a fidelity loss with respect to the fully sampled MRI. Promising results are obtained for brain MRI reconstruction using only 40\%, 25\% and 16.6\% of the data.

The paper is organized as follows. Section \ref{method_section} presents some theoretical foundation and our method. Section \ref{experiments_section} describes the experimental results. Conclusions and future directions are describes in section \ref{conclusions_section}.

%--------------------- METHOD --------------------%
\section{Method}\label{method_section}

@@

Let $s_{p}=M_{p}\odot s_{0}$ denote the under-sampled k-space. Given a sampling mask and a model $f$, defined by the set of parameters $\Theta$, our goal is to estimate the missing k-space samples such that: 
\begin{equation}
\Theta=\arg\min_{\Theta}L(F^{H}f\left(s_{p};\Theta\right),\boldsymbol{u})
\end{equation}
where $L\left(\cdot\right)$ is the loss function. While choosing the loss to be L2 norm is reasonable for natural images, for the k-space, which has different spatial features, this may not be enough. As mentioned in \cite{pathak2016context}, L2 minimization provides a blurry solution, results in a loss of fine details. 
Averaging the high frequency details in the k-space domain results in very poor reconstruction. In order to address this problem, we used the adversarial loss, based on GAN.

@@

\begin{equation}
\begin{aligned}L_{G}=\alpha\cdot E_{\mathrm{z\sim p_{u}\left(z\right)}}\mathrm{\log\left[1-D\left(F^{-1}\left(\hat{s}_{0}\right)\right)\right]}+\\
\beta\cdot||\left(1-M_{p}\right)\odot\left(\hat{s}_{0}-s_{0}\right)||_{2}^{2}
\end{aligned}
\end{equation}
where $\hat{s}_{0}$ is the estimated k-space and $\alpha=1,\,\beta=1$ are hyperparameters tuned by a cross-validation process. The discriminator's input is the reconstructed MR image,\textbf{ }i.e.,\textbf{ }after IFFT. By that, we are integrating the reconstruction phase in our optimization.
In this work, we use the Wasserstein distance as the GAN loss function~\cite{arjovsky2017wasserstein} which helps us to improve the training stability and provides better reconstruction than the classic GAN.

@@

A common architecture is used for the discriminator, composed of convolutional layers, batch normalization, and leaky-ReLU as suggested in \cite{radford2015unsupervised}. For the generator, we compose a dedicated architecture based on multi-channel input for representing the real and imaginary components. Both architectures are shown in Figure \ref{fig:test}.\textbf{ }The training methodology is doing $k_{d}$ discriminator update steps for each generator single step.

@@

%--------------------- Experiments --------------------%
\section{Experiments}\label{experiments_section}

@@

We compare the proposed method to reconstruction results obtained by using a conventional compressed sensing method CS-MRI \cite{lustig2007sparse} and Zero-filling. In addition, we optimized two networks: 1. CNN-L2 - a k-space generator (with same architecture as the proposed method) using only L2 loss. 2. IM-CNN-L2 - a network which performs on the image-space and optimized to remove the artifacts caused by under-sampling and zero padding. 
%We used the U-net \cite{ronneberger2015u} architecture inspired by \cite{lee2017deep}. 
We used the U-net \cite{ronneberger2015u} architecture and the same reconstruction method as presented in~\cite{hyun2017deep}. Specifically, we apply an FFT on the U-net image to get an estimated k-space. The fully k-space is then recovered by integrating the sampled k-space according to the sampling mask.
The same sampling masks was used for all cases.

@@

%--------------------- CONCLUSIONS --------------------%
\section{Discussion}\label{conclusions_section}
